The regularity of ODEs and thimble integrals \\ with respect to Borel summation \begin{draft}\textbf{[DRAFT]}\end{draft}

### 2024-11-13 borel-regularity.tex
Rewrite cantilever thimble integral argument

\begin{scope}[shift={(5.5, 0)}]
\begin{fiber}
\fill[pwbeige!30, draw=pwbeige!60] (-\phase-\spread:\dis) +(-\phase-\spread-90:\rshade) -- +(0, 0) arc (-\phase-\spread:-\phase+\spread:\dis) -- ++(-\phase+\spread+90:\rshade) -- (\rshade, \rshade) -- (\rshade, -\rshade) -- (0, -\rshade) -- cycle;
\genfibercontent[dual]
\node[anchor=north west, inner sep=2mm] at (-\rfiber, \rfiber) {$z$};
\end{fiber}
\end{scope}
\end{tikzpicture}
\captionof{figure}{A sector $\Omega_\alpha$ in the position domain, and the corresponding union of half-planes $\widehat{\Omega}_\alpha^\Lambda$ in the frequency domain.}\label{fig:sectorial_domain-pos-fre}
\end{center}
To describe the image of the Laplace transform $\laplace_{\zeta,\alpha}$, we introduce frequency-domain counterparts for the function spaces $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ from Definition~\ref{def:HL_inf}.
%
\begin{definition}\label{def:H_hat}
Let $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ be the space of holomorphic functions $\Phi$ on $\widehat{\Omega}_\alpha^\Lambda$ with $|\Phi| \lesssim \Delta^\sigma$, where $\Delta$ is the function that measures distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$. The norm $\|\Phi\|_{\sigma, \Lambda} = \sup_{\widehat{\Omega}_\alpha^\Lambda} \Delta^{-\sigma} |\Phi|$ turns $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ into a Banach space.    
\end{definition}
To make statements about $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ that hold when $\Lambda$ is large enough, it is helpful to have a space that encompasses $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ for all $\Lambda$. Since restriction gives an inclusion $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda) \hookrightarrow \dualsingexp{\sigma}(\widehat{\Omega}_\alpha^{\Lambda'})$ whenever $\Lambda < \Lambda'$, we can define a colimit space $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\bullet)$ that all of the spaces $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ include into.
%
\begin{prop}[Following~\cite{sternin1995borel}]\label{prop:laplace-cont}
Let $\Omega_\alpha$ be an open sector with $\zeta = \alpha$ at its tip, and an opening angle of $\pi$ or less. For any $\sigma > 0$ and $\Lambda \ge 0$, and any angle $\theta$ in the opening of $\Omega_\alpha$, the Laplace transform $\laplace_{\zeta_\alpha, 0}^\theta$ is a continuous map $\singexp{\sigma-1}{\Lambda}(\Omega_\alpha) \to \dualsingexp{-\sigma}(\widehat{\Omega}_\alpha^\Lambda)$, with a norm of at most $\Gamma(\sigma)$.
\end{prop}
\begin{proof}
Given some $\phi \in \singexp{\sigma-1}{\Lambda}(\Omega_\alpha)$, we compute
\begin{align*}
|\laplace_{\zeta_\alpha, 0}^\theta \phi| & = \left| \int_{\mathcal{J}_{\zeta_\alpha, 0}^\theta} e^{-z\zeta_\alpha} \phi\,d\zeta_\alpha \right| \\
& \le \int_{\mathcal{J}_{\zeta_\alpha,0}^\theta} e^{-\Re(z\zeta_\alpha)} |\zeta_\alpha|^{\sigma-1} e^{\Lambda |\zeta_\alpha|} \|\phi\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha| \\
& \le \int_{\mathcal{J}_{\zeta_\alpha,0}^\theta} e^{(\Lambda - c_{z, \theta}|z|)|\zeta_\alpha|} |\zeta_\alpha|^{\sigma-1} \|\phi\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha|,
\end{align*}
where $c_{z, \theta}$ is the cosine of $\arg(z) + \theta$. When $|z|$ is large and $c_{z, \theta}$ is positive, the integrand shrinks exponentially as $|\zeta|$ grows. This shows that for each angle $\theta$ in the opening of $\Omega_\alpha$, the integral defining $\laplace_{\zeta_\alpha, 0}^\theta \phi$ converges in some region of $\widehat{\Omega}_\alpha^\Lambda$. It also shows that for different angles $\theta$, the functions $\laplace_{\zeta_\alpha, 0}^\theta \phi$ match where their domains overlap. We can therefore glue these functions together into one big Laplace transform of $\phi$, defined at large values of $|z|$ across the whole opening angle of $\widehat{\Omega}_\alpha^\Lambda$.

We can now simplify the calculation of $\laplace_{\zeta_\alpha, 0}^\theta \phi$ by looking at $\arg(z)$ and using the closest angle $\theta$ in the opening of $\Omega_\alpha$. This keeps $\Lambda - c_{z, \theta}|z|$ equal to $\Delta$, the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$. It follows that
\begin{align*}
|\laplace_{\zeta_\alpha, 0}^\theta \phi| & \le \int_{\mathcal{J}_{\zeta_\alpha, 0}^{\arg(z)}} e^{-\Delta|\zeta_\alpha|} |\zeta_\alpha|^{\sigma-1} \|\phi\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha| \\
& = \int_0^\infty e^{-\Delta t} t^{\sigma-1} \|\phi\|_{\sigma-1, \Lambda}\,dt.
\end{align*}
The integral on the last line converges throughout $\widehat{\Omega}_\alpha^\Lambda$. We can evaluate it by observing that it is a Laplace transform integral, with the roles of position and frequency played by $t$ and $\Delta$ respectively:
\[ |\laplace_{\zeta_\alpha, 0}^\theta \phi| \le \Gamma(\sigma) \Delta^{-\sigma} \|\phi\|_{\sigma-1, \Lambda}. \]
In terms of the metric on $\dualsingexp{-\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ defined above, this bound says that
\[ \|\laplace_{\zeta_\alpha, 0}^\theta \phi\|_{-\sigma, \Lambda} \le \Gamma(\sigma) \|\phi\|_{\sigma-1, \Lambda}, \]
which is what we wanted to show.
\end{proof}
\begin{prop}\label{prop:inverse_laplace_analytic}
Let $\Omega_\alpha$ be an open sector with tip $\zeta = \alpha$ and opening angle $\Theta \le \pi$, and let $\Lambda' = \Lambda / \cos(\Theta)$.\textcolor{red}{Who is $\Lambda$? Add assumption on $\sigma$} Under the conditions of Proposition~\ref{prop:laplace-cont}, for any $\varepsilon \in (0, \tfrac{\Theta}{2})$, the Laplace transform
\[ \laplace_{\zeta_\alpha, 0}^\theta \maps \singexp{\sigma-1}{\Lambda}(\Omega_\alpha) \to \dualsingexp{-\sigma}(\widehat{\Omega}_\alpha^\Lambda) \]
has a continuous left inverse
\[ \left(\laplace_{\zeta_\alpha, 0}^\theta\right)^{-1} \maps \dualsingexp{-\sigma}(\widehat{\Omega}_\alpha^\Lambda) \to \singexp{\sigma-1}{\Lambda'}(\Omega_\alpha^\varepsilon), \]
with a norm of at most
\[ \frac{\Gamma(1-\sigma)}{\pi\,\sin(\varepsilon/2)}. \]
Here, $\Omega_\alpha^\varepsilon \subset \Omega_\alpha$ is the open sector created by cutting a sector of angle $\varepsilon$ off each edge of $\Omega_\alpha$.
\end{prop}
\begin{proof}
The boundary of $\widehat{\Omega}_\alpha^\Lambda$ consists of two rays connected by a circular arc. Extend the rays until they meet, forming the boundary of a sector with opening angle $\pi - \Theta$. Expand that sector by angle $\varepsilon/2$ on both sides. The edges of the expanded sector form a path $\mathcal{C}$ within $\widehat{\Omega}_\alpha^\Lambda$, as shown in Figure~\ref{fig:ref-path}.
\begin{center}
\begin{tikzpicture}
\setfiberscale{2.5}
\pgfmathsetmacro{\rshade}{1.5*\rfiber}
\newcommand{\dis}{1.25}
\renewcommand{\phase}{0}
\newcommand{\spread}{55.5}
\pgfmathsetmacro{\peakdis}{\dis / cos(\spread)}

@@

% coordinate label
\node[anchor=north west, inner sep=2mm] at (-\rfiber, \rfiber) {$z$};
\end{fiber}
\end{tikzpicture}
\captionof{figure}{The thick black line is the path $\mathcal{C}$.}\label{fig:ref-path}
\end{center}
Parameterize $\mathcal{C}$ using the arc length parameter $t$ which is zero at the midpoint of the circular arc part of $\mathcal{C}$. The path $\mathcal{C}$ is made of two rays, which meet at an angle of $\pi - \Theta + \varepsilon$. Parameterize it using the arc length parameter $t$ which is zero where the rays meet. Along $\mathcal{C}$, the distance $\Delta$ to the boundary of $\widehat{\Omega}_\alpha^\Lambda$ satisfies the estimate
\[ \Delta \ge \sin(\varepsilon/2)\,|t|\,, \]
as shown in Figure~\ref{fig:ref-path}. On $\Omega_\alpha^\varepsilon \times \mathcal{C}$, we have
\[ \Re(z\zeta_\alpha) \le |\zeta_\alpha| \big(\Lambda' - \sin(\varepsilon/2)\,|t|\big)\,. \]
\begin{todo}[Justify bounds in words.]\end{todo}
\begin{center}
\begin{tikzpicture}
\setfiberscale{2.5}
\pgfmathsetmacro{\rshade}{1.5*\rfiber}
\newcommand{\dis}{1.25}
\renewcommand{\phase}{0}
\newcommand{\spread}{55.5}
\pgfmathsetmacro{\peakdis}{\dis / cos(\spread)}

@@

% point at node boundary
\begin{scope}[pwbeige!80!black]
\draw[out=165, in=30, -stealth] (3.0, 1.8) node[anchor=west, inner sep=1] {$\Re\big(z\tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) = \Lambda'$} to (1.9, 1.6);
\draw[out=-100, in=110, shorten >=0.5mm, -stealth] (1.1, 2.8) node[anchor=south, inner sep=0.5] {$t \sin(\tfrac{\varepsilon}{2})$} to (dist-anchor);
\end{scope}
\end{tikzpicture}
\captionof{figure}{\begin{todo}[\ldots] Mention that the phase of $\zeta_\alpha$ has been chosen to bring the line $\Re\big(z\tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) = \Lambda'$ as close as possible to $\mathcal{C}$.\end{todo}}
\end{center}

@@

Because of the conditions we put on $\Omega$, we can apply Proposition~\ref{prop:laplace-cont}, which tells us that $E_n$ lies in $\dualsingexp{-\rho-n-1}(\widehat{\Omega}_0^\Lambda)$. This means that $|E_n| \lesssim \Delta^{-\rho-n-1}$, where $\Delta$ is the distance to the boundary of $\widehat{\Omega}_0^\Lambda$. \begin{revised}Observe that $\widehat{\Omega}_0^\Lambda$ is a union of half-planes, the distance to the boundary of each half-plane increases linearly along any ray that intersects the half-plane, and $\Delta$ is the infimum of these distances. From this, we can deduce that $|z|/\Delta$ goes to a constant limit as $z \to \infty$ along any ray that intersects $\widehat{\Omega}_0^\Lambda$.\end{revised}\footnote{The constant limit is not uniform over all rays, so we are showing that $\Phi$ is asymptotic, but not necessarily uniformly asymptotic, to $\series{\Phi}$.} We then reason that
\begin{align*}
|z^{\rho+n} E_n| & \lesssim |z|^{\rho+n} \Delta^{-\rho-n-1} \\
& = \big(|z|/\Delta\big)^{\rho+n} \Delta^{-1} \\
& \lesssim \Delta^{-1}
\end{align*}
along any ray \begin{revised}that intersects $\widehat{\Omega}_0^\Lambda$\end{revised}. This, as discussed above, proves the desired result.
\end{proof}
\color{black}

@@

where $\mathcal{C}_a^\theta(\zeta)$ is the part of $\mathcal{C}_a^\theta$ that goes through $f^{-1}([\alpha,\zeta e^{i\theta}])$. Notice that $\mathcal{C}_a^\theta(\zeta)$ starts and ends in $f^{-1}(\zeta)$.

@@

If we had a thimble integral expression for $V_\alpha$, we could use the thimble projection formula, as written in equation~\eqref{eqn:formula-proof}, to find $v_\text{uni}$. Since we found $v_\text{uni}$ in Section~\ref{sec:solve-cantilever-eqn}, we can work backwards from equation~\eqref{thimble-difference} to guess a thimble integral expression for $V_\alpha$. \begin{todo}[Do the argument in reverse, starting with the expression that looks like $v_\text{uni}$]\end{todo}

@@

Equation~\eqref{eqn:formula-proof} becomes
\[ \frac{1}{\sqrt{\zeta^4-\omega^2}} = \frac{\partial}{\partial \zeta} \left( \int_{\mathcal{C}_a^\theta(\zeta)}\,du \right). \]
\[ \frac{d\zeta}{\sqrt{\zeta^4-\omega^2}} = \frac{\partial}{\partial \zeta} \left( \int_{\mathcal{C}_a^\theta(\zeta)}\,du \right)d\zeta. \]
\[ \frac{d\zeta}{\sqrt{\zeta^4-\omega^2}} = d\Big[ \left( \int_{\mathcal{C}_a^\theta(\zeta)}\,du \right)\Big]. \]
If we guess that $\operatorname{start} \mathcal{C}_a^\theta(\zeta) = -\operatorname{end} \mathcal{C}_a^\theta(\zeta)$, we can rewrite the equation above as
\[ \frac{1}{2}\left[\frac{d\zeta}{\sqrt{\zeta^4 - \omega^2}}\right] = \frac{\partial}{\partial \zeta} \left( \int_{\mathcal{C}_a^\theta(\zeta)}\,du \right). \]

>>>>

\begin{scope}[shift={(5.5, 0)}]
\begin{fiber}
\fill[pwbeige!30, draw=pwbeige!60] (-\phase-\spread:\dis) +(-\phase-\spread-90:\rshade) -- +(0, 0) arc (-\phase-\spread:-\phase+\spread:\dis) -- ++(-\phase+\spread+90:\rshade) -- (\rshade, \rshade) -- (\rshade, -\rshade) -- (0, -\rshade) -- cycle;
\genfibercontent[dual]
\node[anchor=north west, inner sep=2mm] at (-\rfiber, \rfiber) {$z$};
\end{fiber}
\end{scope}
\end{tikzpicture}
\captionof{figure}{A sector $\Omega_\alpha$ in the position domain, and the corresponding union of half-planes $\widehat{\Omega}_\alpha^\Lambda$ in the frequency domain.}\label{fig:sectorial_domain-pos-fre}
\end{center}
To describe the image of the Laplace transform $\laplace_{\zeta,\alpha}$, we introduce frequency-domain counterparts for the function spaces $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ from Definition~\ref{def:HL_inf}.
%
\begin{definition}\label{def:H_hat}
Let $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ be the space of holomorphic functions $\Phi$ on $\widehat{\Omega}_\alpha^\Lambda$ with $|\Phi| \lesssim \Delta^\sigma$, where $\Delta$ is the function that measures distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$. The norm $\|\Phi\|_{\sigma, \Lambda} = \sup_{\widehat{\Omega}_\alpha^\Lambda} \Delta^{-\sigma} |\Phi|$ turns $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ into a Banach space.    
\end{definition}
To make statements about $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ that hold when $\Lambda$ is large enough, it is helpful to have a space that encompasses $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ for all $\Lambda$. Since restriction gives an inclusion $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda) \hookrightarrow \dualsingexp{\sigma}(\widehat{\Omega}_\alpha^{\Lambda'})$ whenever $\Lambda < \Lambda'$, we can define a colimit space $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\bullet)$ that all of the spaces $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ include into.
%
\begin{prop}[Following~\cite{sternin1995borel}]\label{prop:laplace-cont}
Let $\Omega_\alpha$ be an open sector with $\zeta = \alpha$ at its tip, and an opening angle of $\pi$ or less. For any $\sigma > 0$ and $\Lambda \ge 0$, and any angle $\theta$ in the opening of $\Omega_\alpha$, the Laplace transform $\laplace_{\zeta_\alpha, 0}^\theta$ is a continuous map $\singexp{\sigma-1}{\Lambda}(\Omega_\alpha) \to \dualsingexp{-\sigma}(\widehat{\Omega}_\alpha^\Lambda)$, with a norm of at most $\Gamma(\sigma)$.
\end{prop}
\begin{proof}
Given some $\phi \in \singexp{\sigma-1}{\Lambda}(\Omega_\alpha)$, we compute
\begin{align*}
|\laplace_{\zeta_\alpha, 0}^\theta \phi| & = \left| \int_{\mathcal{J}_{\zeta_\alpha, 0}^\theta} e^{-z\zeta_\alpha} \phi\,d\zeta_\alpha \right| \\
& \le \int_{\mathcal{J}_{\zeta_\alpha,0}^\theta} e^{-\Re(z\zeta_\alpha)} |\zeta_\alpha|^{\sigma-1} e^{\Lambda |\zeta_\alpha|} \|\phi\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha| \\
& \le \int_{\mathcal{J}_{\zeta_\alpha,0}^\theta} e^{(\Lambda - c_{z, \theta}|z|)|\zeta_\alpha|} |\zeta_\alpha|^{\sigma-1} \|\phi\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha|,
\end{align*}
where $c_{z, \theta} = \cos\big(\arg(z) + \theta\big)$. When $|z|$ is large and $c_{z, \theta}$ is positive, the integrand shrinks exponentially as $|\zeta_\alpha|$ grows. This shows that for each angle $\theta$ in the opening of $\Omega_\alpha$, the integral defining $\laplace_{\zeta_\alpha, 0}^\theta \phi$ converges in some region of $\widehat{\Omega}_\alpha^\Lambda$. It also shows that for different angles $\theta$, the functions $\laplace_{\zeta_\alpha, 0}^\theta \phi$ match where their domains overlap. We can therefore glue these functions together into one big Laplace transform of $\phi$, defined at large values of $|z|$ across the whole opening angle of $\widehat{\Omega}_\alpha^\Lambda$.

We can now simplify the calculation of $\laplace_{\zeta_\alpha, 0}^\theta \phi$ by looking at $\arg(z)$ and using the closest angle $\theta$ in the opening of $\Omega_\alpha$. This keeps $\Lambda - c_{z, \theta}|z|$ equal to $\Delta$, the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$. It follows that
\begin{align*}
|\laplace_{\zeta_\alpha, 0}^\theta \phi| & \le \int_{\mathcal{J}_{\zeta_\alpha, 0}^{\arg(z)}} e^{-\Delta|\zeta_\alpha|} |\zeta_\alpha|^{\sigma-1} \|\phi\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha| \\
& = \int_0^\infty e^{-\Delta t} t^{\sigma-1} \|\phi\|_{\sigma-1, \Lambda}\,dt.
\end{align*}
The integral on the last line converges throughout $\widehat{\Omega}_\alpha^\Lambda$. We can evaluate it by observing that it is a Laplace transform integral, with the roles of position and frequency played by $t$ and $\Delta$ respectively:
\[ |\laplace_{\zeta_\alpha, 0}^\theta \phi| \le \Gamma(\sigma) \Delta^{-\sigma} \|\phi\|_{\sigma-1, \Lambda}. \]
In terms of the metric on $\dualsingexp{-\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ defined above, this bound says that
\[ \|\laplace_{\zeta_\alpha, 0}^\theta \phi\|_{-\sigma, \Lambda} \le \Gamma(\sigma) \|\phi\|_{\sigma-1, \Lambda}, \]
which is what we wanted to show.
\end{proof}
\begin{prop}\label{prop:inverse_laplace_analytic}
Let $\Omega_\alpha$ be an open sector with tip $\zeta = \alpha$ and opening angle $\Theta \le \pi$. Choose some $\sigma > 0$ and $\Lambda \ge 0$, and let $\Lambda' = \Lambda / \cos(\Theta)$. Under the conditions of Proposition~\ref{prop:laplace-cont}, for any $\varepsilon \in (0, \tfrac{\Theta}{2})$, the Laplace transform
\[ \laplace_{\zeta_\alpha, 0}^\theta \maps \singexp{\sigma-1}{\Lambda}(\Omega_\alpha) \to \dualsingexp{-\sigma}(\widehat{\Omega}_\alpha^\Lambda) \]
has a continuous left inverse
\[ \left(\laplace_{\zeta_\alpha, 0}^\theta\right)^{-1} \maps \dualsingexp{-\sigma}(\widehat{\Omega}_\alpha^\Lambda) \to \singexp{\sigma-1}{\Lambda'}(\Omega_\alpha^\varepsilon), \]
with a norm of at most
\[ \frac{\Gamma(1-\sigma)}{\pi\,\sin(\varepsilon/2)}. \]
Here, $\Omega_\alpha^\varepsilon \subset \Omega_\alpha$ is the open sector created by cutting a sector of angle $\varepsilon$ off each edge of $\Omega_\alpha$.
\end{prop}
\begin{proof}
The boundary of $\widehat{\Omega}_\alpha^\Lambda$ consists of two rays connected by a circular arc. Extend the rays until they meet, forming the boundary of a sector with opening angle $\pi - \Theta$. Expand that sector by angle $\varepsilon/2$ on both sides. The edges of the expanded sector form a path $\mathcal{C}$ within $\widehat{\Omega}_\alpha^\Lambda$, as shown in Figure~\ref{fig:ref-path}.
\begin{center}
\begin{tikzpicture}
\setfiberscale{2.5}
\pgfmathsetmacro{\rshade}{1.5*\rfiber}
\newcommand{\dis}{1.25}
\renewcommand{\phase}{0}
\newcommand{\spread}{55.5}
\pgfmathsetmacro{\peakdis}{\dis / cos(\spread)}

@@

% coordinate label
\node[anchor=north west, inner sep=2mm] at (-\rfiber, \rfiber) {$z$};
\end{fiber}
\end{tikzpicture}
\captionof{figure}{The thick black line is the path $\mathcal{C}$.}\label{fig:ref-path}
\end{center}
Parameterize $\mathcal{C}$ using the arc length parameter $t$ which is zero at the midpoint of the circular arc part of $\mathcal{C}$. The path $\mathcal{C}$ is made of two rays, which meet at an angle of $\pi - \Theta + \varepsilon$. Parameterize it using the arc length parameter $t$ which is zero where the rays meet. Along $\mathcal{C}$, the distance $\Delta$ to the boundary of $\widehat{\Omega}_\alpha^\Lambda$ satisfies the estimate
\[ \Delta \ge \sin(\varepsilon/2)\,|t|\,, \]
as shown in Figure~\ref{fig:ref-path}. On $\Omega_\alpha^\varepsilon \times \mathcal{C}$, we have
\[ \Re(z\zeta_\alpha) \le |\zeta_\alpha| \big(\Lambda' - \sin(\varepsilon/2)\,|t|\big)\,. \]
\begin{todo}[Justify bounds in words: Fix a value of the coordinate $\zeta_\alpha$ representing a point in $\Omega_\alpha^\varepsilon$, and look at the half-plane $\Re\big(z \tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) > \Lambda'$, as shown in Figure~\ref{fig:bound-real-part}. The curve $\mathcal{C}$ lies entirely outside this half-plane, so we have $\Re\big(z \tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) \le \Lambda'$ throughout it. Each of the rays that make up $\mathcal{C}$ makes an angle of at least $\varepsilon/2$ with the boundary line $\Re\big(z \tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) = \Lambda'$. Therefore, as we move along the curve $\mathcal{C}$, the distance to the boundary of the half-plane $\Re\big(z \tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) > \Lambda'$ increases at rate $\sin(\tfrac{\varepsilon}{2})$ with respect to the arc length parameter $t$.]\end{todo}
\begin{center}
\begin{tikzpicture}
\setfiberscale{2.5}
\pgfmathsetmacro{\rshade}{1.5*\rfiber}
\newcommand{\dis}{1.25}
\renewcommand{\phase}{0}
\newcommand{\spread}{55.5}
\pgfmathsetmacro{\peakdis}{\dis / cos(\spread)}

@@

% point at node boundary
\begin{scope}[pwbeige!80!black]
\draw[out=165, in=30, -stealth] (3.0, 1.8) node[anchor=west, inner sep=1] {$\Re\big(z\tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) = \Lambda'$} to (1.9, 1.6);
\draw[out=-100, in=110, shorten >=0.5mm, -stealth] (1.1, 2.8) node[anchor=south, inner sep=0.5] {$t \sin(\tfrac{\varepsilon}{2})$} to (dist-anchor);
\end{scope}
\end{tikzpicture}
\captionof{figure}{\begin{todo}[\ldots] Polish figure: label half-plane $(>)$ instead of boundary $(=)$. Mention that the phase of $\zeta_\alpha$ has been chosen to bring the line $\Re\big(z\tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) = \Lambda'$ as close as possible to $\mathcal{C}$. Maybe add some figure copies (without the extra label stuff) where the angle of the half-plane varies.\end{todo}}\label{fig:bound-real-part}
\end{center}

@@

Because of the conditions we put on $\Omega$, we can apply Proposition~\ref{prop:laplace-cont}, which tells us that $E_n$ lies in $\dualsingexp{-\rho-n-1}(\widehat{\Omega}_0^\Lambda)$. This means that $|E_n| \lesssim \Delta^{-\rho-n-1}$, where $\Delta$ is the distance to the boundary of $\widehat{\Omega}_0^\Lambda$. Observe that $\widehat{\Omega}_0^\Lambda$ is a union of half-planes, the distance to the boundary of each half-plane increases linearly along any ray that intersects the half-plane, and $\Delta$ is the infimum of these distances. From this, we can deduce that $|z|/\Delta$ goes to a constant limit as $z \to \infty$ along any ray that intersects $\widehat{\Omega}_0^\Lambda$.\footnote{The constant limit is not uniform over all rays, so we are showing that $\Phi$ is asymptotic, but not necessarily uniformly asymptotic, to $\series{\Phi}$.} We then reason that
\begin{align*}
|z^{\rho+n} E_n| & \lesssim |z|^{\rho+n} \Delta^{-\rho-n-1} \\
& = \big(|z|/\Delta\big)^{\rho+n} \Delta^{-1} \\
& \lesssim \Delta^{-1}
\end{align*}
along any ray that intersects $\widehat{\Omega}_0^\Lambda$. This, as discussed above, proves the desired result.
\end{proof}
\color{black}

@@

where $\mathcal{C}_a^\theta(\zeta)$ is the part of $\mathcal{C}_a^\theta$ that goes through $f^{-1}\big([\alpha,\zeta e^{i\theta}]\big)$. Notice that $\mathcal{C}_a^\theta(\zeta)$ starts and ends in $f^{-1}(\zeta)$.

@@

If we had a thimble integral expression for $V_\alpha$, we could use the thimble projection formula, as written in equation~\eqref{eqn:formula-proof}, to find $v_\text{uni}$. Since we found $v_\text{uni}$ in Section~\ref{sec:solve-cantilever-eqn}, we can work backwards from equation~\eqref{thimble-difference} to guess a thimble integral expression for $V_\alpha$.

@@

We hope to express $V_\alpha$ in the form
\[ \int_{\mathcal{C}_a^\theta}e^{-z f} du, \]
where $f$ is a holomorphic function on $\C$, $u$ is the standard coordinate on $\C$, $a$ is a critical point of $f$ with $f(a) = \alpha$, and $\mathcal{C}_a^\theta$ is the component of $f^{-1}\big(\alpha + e^{i\theta}[0, \infty)\big)$ that runs through $a$. We know from equation~\eqref{thimble-difference} that this thimble integral will evaluate to $V_\alpha$ as long as
\begin{equation}\label{eqn:cantilever-thimble-difference}
\frac{1}{\sqrt{\zeta^4-\omega^2}} = \left[\frac{du}{df}\right]_{\operatorname{start} \mathcal{C}_a^\theta(\zeta)}^{\operatorname{end} \mathcal{C}_a^\theta(\zeta)},
where $\mathcal{C}_a^\theta(\zeta)$ is the part of $\mathcal{C}_a^\theta$ that goes through $f^{-1}\big([\alpha,\zeta e^{i\theta}]\big)$. Recognizing the left-hand side, $v_\text{uni}$, as the integrand of an elliptic integral, we guess that
\[ f = 2i\omega \operatorname{sd}\big(u, \tfrac{1}{\sqrt{2}}\big)\,, \]
since the Jacobi elliptic function $\operatorname{sd}$ is the inverse of an incomplete elliptic integral. To confirm that this equation~\eqref{eqn:cantilever-thimble-difference} holds for this guess, we first use Jacobi's transformations to rewrite $f$ in terms of $\operatorname{sn}$:
\[ f = \omega^{1/2} \operatorname{sn}\big(2i \omega^{1/2} u, i\big)\,. \]
In terms of the incomplete elliptic integral
\[ F(x; k) := \int_0^x \frac{dt}{\sqrt{(1-t^2)(1-k^2t^2)}}\,, \]
we then have
F(\omega^{-1/2} f; i) & = 2i \omega^{1/2} u \\
\frac{\omega^{-1/2}\;df}{\sqrt{1 - (\omega^{-1/2} f)^4}} & = 2i \omega^{1/2}\;du \\
\frac{1}{2i \omega \sqrt{1 - \omega^{-2} f^4}} & = \frac{du}{df}\,.
We can simplify this to
\[ \frac{1}{2}\left[\frac{1}{\sqrt{f^4 - \omega^2}}\right] = \frac{du}{df} \]
by taking the branch of $\sqrt{f^4 - \omega^2}$ that evaluates to $i\omega$ when $f = 0$. By definition, $f\big(\operatorname{end} \mathcal{C}_a^\theta(\zeta)\big) = \zeta$
so we have
\begin{equation}\label{eqn:cantilever-endpoint}
\frac{1}{2}\left[\frac{1}{\sqrt{\zeta^4 - \omega^2}}\right] = \left.\frac{du}{df}\right|_{\operatorname{end} \mathcal{C}_a^\theta(\zeta)}\,,
with the branch of the square root determined by analytic continuation along $\mathcal{C}_a^\theta$ from $a$.

From our formula for $f$ in terms of $\operatorname{sd}$, we can see that $f$ is odd at $a$ with respect to $u$, implying that
\[ \left.\frac{du}{df}\right|_{\operatorname{start} \mathcal{C}_a^\theta(\zeta)} = -\left.\frac{du}{df}\right|_{\operatorname{end} \mathcal{C}_a^\theta(\zeta)}\,. \]
We can therefore rewrite equation~\eqref{eqn:cantilever-endpoint} as
\[ \frac{1}{\sqrt{\zeta^4-\omega^2}} = \left[\frac{du}{df}\right]_{\operatorname{start} \mathcal{C}_a^\theta(\zeta)}^{\operatorname{end} \mathcal{C}_a^\theta(\zeta)}\,, \]
confirming that our guess for $f$ satisfies equation~\eqref{eqn:cantilever-thimble-difference}. It follows that
\[ V_\alpha = \int_{\mathcal{C}_a^\theta} \exp\left[ -z\,2i\omega \operatorname{sd}\big(u, \tfrac{1}{\sqrt{2}}\big) \right]\;du. \]

%%Knowing that the inverse of $\operatorname{sn}$ is the incomplete elliptic integral
%%\begin{equation}
%%F(x;k):=\int_0^x \frac{dt}{\sqrt{(1-t^2)(1-k^2t^2)}}\,,
%%\end{equation}
\end{revised}

\begin{draft}
Equation~\eqref{eqn:formula-proof} becomes
\[ \frac{1}{\sqrt{\zeta^4-\omega^2}} = \frac{\partial}{\partial \zeta} \left( \int_{\mathcal{C}_a^\theta(\zeta)}\,du \right). \]
\[ \frac{d\zeta}{\sqrt{\zeta^4-\omega^2}} = \frac{\partial}{\partial \zeta} \left( \int_{\mathcal{C}_a^\theta(\zeta)}\,du \right)d\zeta. \]
\[ \frac{d\zeta}{\sqrt{\zeta^4-\omega^2}} = d\Big[ \left( \int_{\mathcal{C}_a^\theta(\zeta)}\,du \right)\Big]. \]
If we guess that $\operatorname{start} \mathcal{C}_a^\theta(\zeta) = -\operatorname{end} \mathcal{C}_a^\theta(\zeta)$, we can rewrite the equation above as
\[ \frac{1}{2}\left[\frac{d\zeta}{\sqrt{\zeta^4 - \omega^2}}\right] = \frac{\partial}{\partial \zeta} \left( \int_{\mathcal{C}_a^\theta(\zeta)}\,du \right). \]
\end{draft}
